\documentclass[11pt,letterpaper]{article}

% Match website font: PT Serif
\usepackage[T1]{fontenc}
\usepackage{PTSerif}
\usepackage{microtype}

% Page layout with left margin reserved for section labels
\usepackage[
  letterpaper,
  textwidth=5.8in,
  textheight=8.8in,
  marginparwidth=1.2in,
  marginparsep=0.2in,
  left=1.9in,
  top=0.9in,
]{geometry}
\reversemarginpar

\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{ragged2e}
\usepackage{needspace}

\definecolor{labelgray}{gray}{0.45}
\hypersetup{colorlinks=true, urlcolor=blue, linkcolor=blue}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\fancyfoot[R]{\small\itshape Curriculum Vitae, Minjin Chae, \thepage}

\newcommand{\cvsection}[1]{%
  \par\addvspace{1.2em}%
  \noindent\llap{%
    \smash{\parbox[t]{1.2in}{%
      \hyphenpenalty=10000\exhyphenpenalty=10000%
      \RaggedRight\textcolor{labelgray}{\small\strut #1}%
    }}%
    \hspace{0.2in}%
  }\ignorespaces%
}

\setlist{leftmargin=1.5em, topsep=2pt, partopsep=0pt, itemsep=2pt, parsep=0pt}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.7em}
\hyphenation{Division}

\begin{document}

\noindent\hspace*{-1.4in}{\huge Minjin Chae}\par
\bigskip

\cvsection{Contact information}
\begin{minipage}[t]{0.5\linewidth}
432 William James Hall\\
33 Kirkland St.\\
Cambridge, MA 02138
\end{minipage}%
\hfill
\begin{minipage}[t]{0.45\linewidth}
\raggedleft
\href{mailto:minjinchae@g.harvard.edu}{minjinchae@g.harvard.edu}\\
\url{https://chaeminjin.github.io/}
\end{minipage}

\cvsection{Education}
\textbf{Harvard University}\\
Ph.D. in Sociology, 2027 (expected)\\
Dissertation: \emph{Flexible Work, Durable Inequality: Gender, Race, and the Remaking of Workplace Advantage}\\
Committee: David Pedulla (chair), Daniel Schneider, Alexandra Killewald\\
M.A. in Sociology, 2023

\medskip
\textbf{Seoul National University}\\
M.A. in Sociology, 2019\\
B.A. in History Education and B.B.A. in Business, 2017

\cvsection{Research interests}
future of work, organization, social inequality, gender and family

\cvsection{Working papers}
Chae, Minjin. ``When Does Gender Trump Flexibility? Workplace Flexibility and Domestic Task Assignment.'' Under review.
\begin{itemize}
\item Nominated, Best Student Paper Award, Organization and Management Theory Division, Academy of Management, 2026
\end{itemize}

\cvsection{Work in progress}
Chae, Minjin. ``Activating Inequality: Task Segregation and the Racial and Gender Divide in Remote Work.''

Chae, Minjin. ``When Do Firms Reduce or Reproduce Gender Inequality? Organizational Contexts of the Pandemic Work From Home and KiF\"oG Childcare Expansions.''
\begin{itemize}
\item Guest Researcher in residence, WZB Berlin Social Science Center, hosted by Lena Hipp, Spring 2026
\end{itemize}

Chae, Minjin. ``Worker Power and Temporal Rents: How Occupational Closure and Productivity Constraints Shape Schedule Control.''

Cha, Youngjoo, Kaitlin Johnson, and Minjin Chae. ``Why Is the Gender Wage Gap Larger in Some Occupations than Others? Work Hours, Task Flexibility, and the Gender Wage Gap Across Occupations.''

Chae, Minjin. ``Who Works From Home Within the Same Job? Racial Inequality in Remote Work and the Role of Collective Bargaining.''

\needspace{8\baselineskip}
Chae, Minjin. ``Gender Essentialist Norms and Skeptical Attitudes Toward Marriage Among South Korean Young Adults.''
\begin{itemize}
\item International Conference on Sociology of Korea Student Paper Award, University of Pennsylvania Kim Center for Korean Studies, 2022
\item Best Graduate Student Paper Award, The Population Association of Korea, 2019
\end{itemize}

\cvsection{Presentations}
\textit{Occupational Segregation and Remote Work Inequality by Race and Gender, 2017--2026}
\begin{itemize}
\item American Sociological Association Annual Meeting. New York City, US. August 2026.
\item Research Committee 28 of the International Sociology Association. New York City, US. August 2026.
\end{itemize}

\medskip
\textit{Can Workplace Flexibility Policies Promote Gender Equality at Home?}
\begin{itemize}
\item Academy of Management Annual Meeting. Philadelphia, US. August 2026.
\item Work and Family Researcher Network Conference. Montreal, Canada. June 2026.
\item Research Committee 28 of the International Sociology Association. Seville, Spain. May 2026.
\item American Sociological Association Annual Meeting. Chicago, US. August 2025.
\item International Community, Work and Family Conference. Bielefeld, Germany. March 2025.
\item 2024 Second Biannual Korean Sociological Conference. Seoul, South Korea. December 2024.
\end{itemize}

\medskip
\textit{How Worker Power and Time-related Productivity Constraints Shape Schedule Quality}
\begin{itemize}
\item American Sociological Association Annual Meeting. Montreal, Canada. August 2024.
\item American Sociological Association Annual Meeting. Philadelphia, US. August 2023.
\item Korea Inequality Research Network Colloquium. Chuncheon, South Korea. July 2023.
\end{itemize}

\medskip
\textit{The Role of Work Hours and Occupation in the Gender Wage Gap}
\begin{itemize}
\item Work and Family Researcher Network Conference. Montreal, Canada. June 2024.
\end{itemize}

\medskip
\textit{Gender Essentialist Norms and Skeptical Attitudes Toward Marriage Among South Korean Young Adults}
\begin{itemize}
\item International Conference on Sociology of Korea. Philadelphia, US. October 2022.
\item The Population Association of Korea Bi-Annual Meeting. Daejeon, South Korea. June 2019.
\end{itemize}

\cvsection{Other publications}
Yun, Youngho, Yeani Choi, and Minjin Chae. 2021. ``Development and Validity Testing of the Workplace Parentship Index (WPI): Assessment of Family-Friendly Practices.'' \emph{Journal of Occupational and Environmental Medicine} 63(12).

\cvsection{Honors \& Awards}
Nominated, Best Student Paper Award, Organization and Management Theory Division, Academy of Management, 2026

Doctoral Consortium, Organization and Management Theory Division, Academy of Management, 2026

Teaching Certificate, Derek Bok Center for Teaching and Learning, Harvard University, 2026

International Conference on Sociology of Korea Student Paper Award, University of Pennsylvania Kim Center for Korean Studies, 2022

Best Graduate Student Paper Award, The Population Association of Korea, 2019

2nd Prize, Student Paper Competition, Institute for Peace and Unification Studies, Seoul National University, 2017

Grand Prize, Undergraduate Student Paper Competition, The Korean Society for Chinese Studies, 2014

\cvsection{Fellowships \& Grants}
Dissertation Completion Fellowship (\$55{,}000), Harvard University Graduate School of Arts and Sciences, 2026--2027

Graduate Seed Grant (\$1{,}000), Harvard University Center for American Political Studies, 2026

Summer Research Grant (\$1{,}000), Harvard Griffin GSAS Student Council, 2026

Krupp Foundation Dissertation Research Fellowship (\$19{,}000), Minda de Gunzburg Center for European Studies, Harvard University, 2026

Travel Grant, Harvard Center for Population and Development Studies, 2024--2026

Travel Grant, Harvard University Department of Sociology, 2022--2026

Merit/Graduate Society Term-Time Research Fellowship (\$21{,}000), Harvard University Graduate School of Arts and Sciences, 2025

Jens Aubrey Westengard Fund (\$800), Harvard University Graduate School of Arts and Sciences, 2025

Student Scholarship (\$3{,}000), Seoul National University Alumni Association of New England, 2025

Dissertation Research Grant (\$3{,}000), Harvard Center for Population and Development Studies, 2024

Research Grant (\$2{,}700), Harvard University Institute for Quantitative Social Science, 2024

Travel Grant, Harvard University Institute for Quantitative Social Science, 2024, 2025

Graduate Seed Grant (\$750), Harvard University Center for American Political Studies, 2023

Summer Institute in Computational Social Science Research Grant (\$750), Korea Development Institute School of Public Policy and Management, 2022

Division of Social Science Fund (\$500), Harvard University Graduate School of Arts and Sciences, 2022

Community Researcher Grant, Seoul Metropolitan Government, 2019

Lecture and Research Scholarship, Seoul National University Department of Sociology, 2018

Naum Scholarship, Seoul National University Department of Sociology, 2017

SNU Undergraduate Research Program Grant, Seoul National University, 2016

Study Abroad Program Grant, Seoul National University Office of International Affairs, 2016

Merit-Based Scholarship, Seoul National University, 2013--2015

SNU Development Fund Scholarship, Seoul National University, 2013

\cvsection{Teaching}
\textbf{Teaching Fellow, Harvard University}
\begin{itemize}
\item SOC 1136: Work and Culture. Fall 2024.
\item SOC 1128: Models of Social Science Research. Spring 2022, 2023.
\item SOC 1000: Introduction to Sociology. Fall 2022, 2023.
\end{itemize}

\textbf{Undergraduate Thesis Advisor, Harvard University}
\begin{itemize}
\item Jenna Hong
\item Mira Nalbandian
\end{itemize}

\cvsection{Service}
Member, Committee on Higher Degrees, Department of Sociology, Harvard University, 2025--2026

Member, Department Colloquium Committee, Department of Sociology, Harvard University, 2024--2025

Social Chair, Graduate Student Organization, Department of Sociology, Harvard University, 2022--2024

Member, American Sociological Association, Academy of Management, Work Family Researchers Network, Research Committee 28 of the International Sociology Association.

\cvsection{References}
\begin{tabular}[t]{@{}p{0.48\linewidth}p{0.48\linewidth}@{}}
David Pedulla & Daniel Schneider \\
Department of Sociology & Department of Sociology \\
Harvard University & Harvard University \\
\href{mailto:dpedulla@fas.harvard.edu}{dpedulla@fas.harvard.edu} & \href{mailto:dschneider@hks.harvard.edu}{dschneider@hks.harvard.edu} \\[1em]
Alexandra Killewald & \\
Department of Sociology & \\
University of Michigan & \\
\href{mailto:akillewa@umich.edu}{akillewa@umich.edu} & \\
\end{tabular}

\end{document}
